Self-reported LLM usage and outcomes on a data science project: Evidence from two undergraduate data science courses

### 2025-04-14 paper/paper.qmd
minor edits

To investigate the relationship between students' LLM usage and attitudes and their academic performance, a dataset containing self-reported LLM usage, attitudes towards LLMs, final paper grades, and overall academic performance was constructed. This was based on three components:

@@

Students from a range of years took both courses, but most respondents were in their 3rd or 4th year of study (@tbl-year-dist). The prerequisite two-course sequence is typically completed by students in their second year, which would make it difficult to take either course earlier than their 3rd year.

>>>>

To investigate the relationship between students' LLM usage and attitudes and their academic performance, a dataset containing self-reported LLM usage, personal attitudes towards LLMs, final paper grades, and overall academic performance was constructed. This was based on three components:

@@

Students from a range of years took both courses, but most respondents were in their 3rd or 4th year of study (@tbl-year-dist). A prerequisite two-course sequence in mathematical statistics is typically completed by students in their second year, which would make it difficult to take either course earlier than their 3rd year.
